### 2015-03-20 acknowledgements.tex
a few more updates to the signature page
added quotes back in
final format check, added latest PDF

\begin{center}
ACKNOWLEDGEMENTS\\
~\\
\end{center}

@@

I would also like to acknowledge numerous other people for providing
guidance and support during the process.
I will only use first names, but you know who you are. Thank you to: Jess, Chris, Clay, 
Bob, Todd, Leslie, Mike, and Ralph.

>>>>

\begin{center}
ACKNOWLEDGEMENTS\\
\end{center}

@@

Next, I would like to thank my advisor, Dr. Gary Hatfield, for the encouragement and guidance
along the way.  Also, thank you to Clay, Jess, and Chris for helping me formulate 
the initial idea.

Finally, I would like to thank my Mom for providing a 
final grammatical proof-reading of the dissertation.

### 2015-03-20 appendices.tex
final format check, added latest PDF

    \subsection{REQUIREMENTS SCORES - R CODE}
        \subsubsection{REQUIREMENTS HISTOGRAM}
        \label{app:requirements-hist}
            Figure \ref{fig:req-hist} shows a histogram of the data
            for requirements.  The histogram is based upon the
            fraction $\frac{Scheduled Requirements}{Actual Requirements}$. The
            values where the fraction equals 1 have been left out of the histogram.
            So, the histogram show only the data that did not deliver exactly
            on the number of requirements. Rarely are more requirements actually 
            delivered than what was scheduled.  On the opposite side, the histogram
            bars shrink as they approach zero indicating that it is more common
            to miss a few requirements than all the requirements.

@@

        The following are additional data points that could be tracked for project estimation.
        \begin{easylist}[itemize]
            & Change to Database Structure  
            & Modify Database Data    
            & Create a New Database, number of new databases  
            & Server Configuration Changes Required   
            & New Servers Required   
            & Number of People Involved  
            & Number of (sub)Systems Involved  
            & Estimation Date
            & Number of Days Allowed
            & List of Other Attributes
            & Number of Screens Involved 
            & Actual Values (hours, days, dollars) 
            & Estimated Values
            && Estimated Dev Hours: 
                The number of development hours estimated for a 
                project, this is just developer hours
            && Estimated Doc Hours: 
                The number of documentation hours estimated for a project
            && Estimated Test Hours:
                The number of testing hours estimated for a project
            && Estimated Deployment Hours: 
                The number of estimated hours required to 
                deploy the project
        \end{easylist}

>>>>

    \subsection{REQUIREMENTS SCORES - R CODE}
        \subsubsection{REQUIREMENTS HISTOGRAM}
        \label{app:requirements-hist}
            Figure \ref{fig:req-hist} shows a histogram of the data
            for requirements.  The histogram is based upon the
            fraction, $\frac{Scheduled Requirements}{Actual Requirements}$. The
            values where the fraction equals one have been left out of the histogram.
            So, the histogram show only the data that did not deliver exactly
            on the number of requirements. Rarely are more requirements actually 
            delivered than what was scheduled.  On the opposite side, the histogram
            bars shrink as they approach zero indicating that it is more common
            to miss a few requirements than all the requirements.

@@

        The following are additional data points that could be tracked for project estimation.
        \begin{easylist}[itemize]
            & Change to database structure  
            & Modify database data    
            & Create a new database, number of new databases  
            & Server configuration changes required   
            & New servers required   
            & Number of people involved  
            & Number of (sub)systems involved  
            & Estimation date
            & Number of days allowed
            & List of other attributes
            & Number of screens involved 
            & Actual values (hours, days, dollars) 
            & Estimated values
            && Estimated development hours: 
                The number of development hours estimated for a 
                project, this is just developer hours
            && Estimated documentation hours: 
                The number of documentation hours estimated for a project
            && Estimated testing hours:
                The number of testing hours estimated for a project
            && Estimated deployment hours: 
                The number of estimated hours required to 
                deploy the project
        \end{easylist}

### 2015-03-20 paper_10_intro.tex
final format check, added latest PDF

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occurred for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[defect] ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed testcases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    Software Engineering Method and Theory (SEMAT) is claiming to 
    be the ``new software engineering'' 
    \cite{Jacobson2014}. 
    \nomenclature{SEMAT}{Software Engineering Method and Theory}
    The authors rightfully claim that 
    software engineering lacks
    an underlying theoretical foundation found in other 
    engineering disciplines.  This lack of theory
    has led software engineering to not be engineering, but 
    rather a craft.  The goal of 
    SEMAT is to merge the craftsmanship and engineering to 
    provide a foundation for software
    engineering.  The primary initiative of SEMAT 
    has been the creation of a kernel for 
    software engineering.  The kernel is the minimal set 
    of things common to all software development
    endeavours. The three parts to the kernel are:
    \begin{enumerate}
        \item \textbf{Measurement} - There must exist a means to 
            determine the health and progress of an endeavour.
        \item \textbf{Categorization} -  The activities must progress 
            through categories during an endeavour.
        \item \textbf{Competencies} - Specific competencies will 
            be required for completing activities
    \end{enumerate}

>>>>

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occurred for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[Defect] - ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed testcases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    Software Engineering Method and Theory (SEMAT) is claiming to 
    be the ``new software engineering'' 
    \cite{Jacobson2014}. 
    \nomenclature{SEMAT}{Software Engineering Method and Theory}
    The authors rightfully claim that 
    software engineering lacks
    an underlying theoretical foundation found in other 
    engineering disciplines.  This lack of theory
    has led software engineering to not be engineering, but 
    rather a craft.  The goal of 
    SEMAT is to merge the craftsmanship and engineering to 
    provide a foundation for software
    engineering.  The primary initiative of SEMAT 
    has been the creation of a kernel for 
    software engineering.  The kernel is the minimal set 
    of things common to all software development
    endeavours. The three parts to the kernel are:
    \begin{enumerate}
        \item \textbf{Measurement} - There must exist a means to 
            determine the health and progress of an endeavour.
        \item \textbf{Categorization} -  The activities must progress 
            through categories during an endeavour.
        \item \textbf{Competencies} - Specific competencies will 
            be required for completing activities.
    \end{enumerate}

### 2015-03-20 paper_20_sdo.tex
more grammatical fixes updates to lists in the appendix
final format check, added latest PDF

\subsection{WHAT IS SOFTWARE?}
Numerous definitions can be found for the term \textit{software}.
Software is more than just computer programs. According to Ian Sommerville \cite{Sommerville2001}, 
"Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly."
This is the definition used for the remainder of this dissertation.

@@

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        many commonalities exist among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the implementation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a guideline for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development life cycle.
        \end{description}

        These 5 steps cannot cover everything that needs to be accomplished
        during a project.  They just provide of rough guideline of what needs
        to be completed in order to ensure a more successful software release.
        Appendix \ref{app:detailedSDLC} contains a more detailed list of the
        tasks necessary to complete the software life cycle.

>>>>

\subsection{WHAT IS SOFTWARE?}
Numerous definitions can be found for the term \textit{software}.
Software is more than just computer programs. According to Ian Sommerville \cite{Sommerville2001}, 
``Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly.''
This is the definition used for the remainder of this dissertation.

@@

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        many commonalities exist among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the implementation phase. Here are
        the five common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a guideline for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development life cycle.
        \end{description}

        These five steps cannot cover everything that needs to be accomplished
        during a project.  They just provide of rough guideline of what needs
        to be completed in order to ensure a more successful software release.
        Appendix \ref{app:detailedSDLC} contains a more detailed list of the
        tasks necessary to complete the software life cycle.

### 2015-03-20 paper_70_case-study.tex
final format check, added latest PDF

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/quality_scores.png}
            \caption{CRI QUALITY SCORES}
            \label{fig:quality-scores}
        \end{figure}

@@

        \begin{figure}[hb]
            \centering
            \includegraphics[scale=.3]{images/availability_scores.png}
            \caption{CRI AVAILABILITY SCORES}
            \label{fig:availability-scores}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/schedule_scores.png}
            \caption{CRI SCHEDULE SCORES}
            \label{fig:schedule-scores}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/requirements_scores.png}
            \caption{CRI REQUIREMENTS SCORES}
            \label{fig:requirements-scores}
        \end{figure}

@@

    \subsection{OVERALL}
        Now it is time to combine the scores for the overall CRI.
        Schedule does not have scores for January 2014 or January 2015.
        Presumably, that is because the SDO within the large financial institution
        does not schedule projects to be completed in January. Much of the work
        would need to be completed over Christmas and New Year's Day, but many
        workers take personal time off of work during that time.  Thus some
        organizations will schedule appropriately.  CRI is well suited to
        handle this problem.  Just perform a weighted average over the
        applicable elements.  In this case study, the weights are all equal,
        so CRI is just a straight average.

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/cri_scores.png}
            \caption{CRI SCORES}
            \label{fig:cri-scores}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/sensitivity.png}
            \caption{CRI SENSITIVITY ANALYSIS}
            \label{fig:sensitivity}
        \end{figure}

@@

        Figure \ref{fig:correlation_cri} shows a scatterplot matrix
        for the individual element scores.  No correlation appears
        to exist between any of the elements. The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the four elements analyzed here remain independent.

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/correlation.png}
            \caption{SCATTERPLOT MATRIX OF CRI ELEMENT SCORES}
            \label{fig:correlation_cri}
        \end{figure}

>>>>

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.28]{images/quality_scores.png}
            \caption{CRI QUALITY SCORES}
            \label{fig:quality-scores}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.28]{images/availability_scores.png}
            \caption{CRI AVAILABILITY SCORES}
            \label{fig:availability-scores}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.28]{images/schedule_scores.png}
            \caption{CRI SCHEDULE SCORES}
            \label{fig:schedule-scores}
        \end{figure}

@@

        \begin{figure}[hbt]
            \centering
            \includegraphics[scale=.28]{images/requirements_scores.png}
            \caption{CRI REQUIREMENTS SCORES}
            \label{fig:requirements-scores}
        \end{figure}

@@

    \subsection{OVERALL}
        Now it is time to combine the scores for the overall CRI.
        Schedule does not have scores for January 2014 or January 2015.
        Presumably, that is because the SDO within the large financial institution
        does not schedule projects to be completed in January. Much of the work
        would need to be completed over Christmas and New Year's Day, but many
        workers take personal time off of work during that time.  Thus some
        organizations will schedule appropriately.  CRI is well suited to
        handle this problem.  Just perform a weighted average over the
        applicable elements.  In this case study, the weights are all equal,
        so CRI is a straight average.

        \begin{figure}[hbt]
            \centering
            \includegraphics[scale=.28]{images/cri_scores.png}
            \caption{CRI SCORES}
            \label{fig:cri-scores}
        \end{figure}

@@

        \begin{figure}[hbt]
            \centering
            \includegraphics[scale=.25]{images/sensitivity.png}
            \caption{CRI SENSITIVITY ANALYSIS}
            \label{fig:sensitivity}
        \end{figure}

@@

        Figure \ref{fig:correlation_cri} shows a scatterplot matrix
        for the individual element scores.  There
        is no clear upper or downward trend in any of the graphs.
        Therefore, no correlation appears
        to exist between any of the elements. The missing element,
        satisfaction, is the most likely element to exhibit correlation. 
        That is because lower scores on the other four elements
        will likely result in 
        decreased survey scores, which will result in lower satisfaction
        scores.  Anyhow, the four elements analyzed here remain independent.

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.25]{images/correlation.png}
            \caption{SCATTERPLOT MATRIX OF CRI ELEMENT SCORES}
            \label{fig:correlation_cri}
        \end{figure}
